---
title: "Highly efficient multiplex human T cell engineering without double-strand breaks using Cas9 base editors"
output:
  html_document:
    fig_height: 6
    fig_width: 10
    toc: no
    toc_float:
      collapsed: no
      smooth_scroll: no
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---
### Supplementary Data 2
##### November, 21st, 2018
##### Beau R. Webber†, Cara-lin Lonetree†, Mitchell G. Kluesner, Matthew J. Johnson, Emily J. Pomeroy, Walker S. Lahr, Garrett Draper, Miechaleen Diers, Nicholas J. Slipek, Amber McElroy, Mark J. Osborn, Branden S. Moriarity
##### Department of Pediatrics, Masonic Cancer Center, Center for Genome Engineering, Department of Medicine, Stem Cell Institute, University of Minnesota, Minneapolis, MN, USA


```{r, include=FALSE}
# Load packages required for data analysis
require(dplyr)
require(plyr)
require(ggplot2)
require(magrittr)
library(readxl)
library(scales)
library(printr)
library(readr)
library(knitr)
library(gridExtra)
library(grid)
```


```{r, include=FALSE}
analysis_name = "moriarity_TBE_NGS_compiled_att1"
sample_information_path = "/Users/kluesner/Desktop/Research/NGS/CRISPR-DAV/analysis/moriarity_TBE_NGS_compiled_att1/sample_information.txt"

color_fn = function(x, breaks = seq(0, 100, 1), pallete = c("white","#E3797D")){
  color_fn_tmp2 = grDevices::colorRampPalette(pallete)
  colors_vec = color_fn_tmp2(
    (max(breaks) - min(breaks))/
    ((max(breaks) - min(breaks))/(length(breaks)-1))
    )
  colors_vec[which.min(abs(x - breaks))]
}

window_start = -10
window_end = 23
table_digits = 1
```


```{r, include=FALSE}
# Additional information about where the target base is for each sample. Import using datapasta::df_paste() in command line.
# Conversely, may be good just to pull information from a .tsv file based on what people upload to the NGS analysis submission.
sample_information = read_tsv(sample_information_path)

# This function pulls out the target Cs from the gRNA sequence
# This function assumes that the target base is that which is nearest to position 7
sample_information$target_position = mapply(FUN = function(X){gregexpr(pattern ='c', X) %>% 
    unlist(.) %>% 
    .[which.min(abs(.-7))]}, X = sample_information$guide) %>% 
    unname()

## Filter these samples
#exclude_samples = c(180, 166)
#sample_information %<>% filter(!(number %in% exclude_samples))
```



```{r, include=FALSE}
# Loading the data and initial cleaning and reshaping for analysis
# Need to first run these commands in unix:
  # analysis='moriarity_TBE_2_NGS'
  # mkdir /Users/kluesner/Desktop/Research/NGS/CRISPR-DAV/completed/"$analysis"/snp
  # mkdir /Users/kluesner/Desktop/Research/NGS/CRISPR-DAV/completed/"$analysis"/indel
  # for f in /Users/kluesner/Desktop/Research/NGS/CRISPR-DAV/completed/"$analysis"/*/deliverables/*/Assets/*_snp.xlsx; do (mv "$f"/Users/kluesner/Desktop/Research/NGS/CRISPR-DAV/completed/"$analysis"/snp); done
  # for f in /Users/kluesner/Desktop/Research/NGS/CRISPR-DAV/completed/"$analysis"/*/deliverables/*/Assets/*_len.xlsx; do (mv "$f" /Users/kluesner/Desktop/Research/NGS/CRISPR-DAV/completed/"$analysis"/indel); done

# May need this command
# mv /Users/kluesner/Desktop/Research/NGS/CRISPR-DAV/batch_analysis/moriarity_TBE_2_NGS_att2/*/site.bed/
#    /Users/kluesner/Desktop/Research/NGS/CRISPR-DAV/completed/moriarity_TBE_2_NGS_att2/*/site.bed/

analysis_folder =  paste0("/Users/kluesner/Desktop/Research/NGS/CRISPR-DAV/completed/", analysis_name)
indel_folder = paste0(analysis_folder, "/indel")
snp_folder = paste0(analysis_folder, "/snp")

# Define the bases
ACGT = c("A", "C", "G", "T")
TGCA = c("T", "G", "C", "A")

# A function for appending all of the excel files together
merge_excel = function(folder){
  files = list.files(folder)
  read_excel %>% 
    lapply(FUN = ., X = paste0(folder, "/", files)) %>%
    plyr::ldply()
}

# Save the appended excel files for indels as a df.
indels = merge_excel(indel_folder) %>% 
  inner_join(., sample_information) %>% 
  dplyr::select(-target_position, -Sample) %>% 
  dplyr::rename(Sample = sample_name)

indels_summarized = indels %>% 
  aggregate(ReadCount~Sample*IndelLength, ., sum) %>%
  inner_join(., indels %>% 
               aggregate(ReadCount~Sample, ., sum) %>%
               dplyr::rename('ReadSum' = 'ReadCount')) %>%
  mutate(ReadPerc = ReadCount/ReadSum)

# Save the appended excel files for snps as a df.
snps = merge_excel(snp_folder) %>% 
  inner_join(., sample_information) %>% 
  dplyr::select(-target_position, -Sample) %>% 
  dplyr::rename(Sample = sample_name)

snps = aggregate(pos~Sample, snps, min) %>% 
  dplyr::rename(., 'guide_start' = 'pos') %>%
  inner_join(snps, .) %>%
  mutate(rel_pos = pos-guide_start-11)
snps_cleaned = bind_cols(
  snps %>% tidyr::gather(., key = base, value = ReadCount, A, C, G, T) %>% dplyr::select(-PctA, -PctC, -PctG, -PctT),
  snps %>% tidyr::gather(., key = base, value = ReadPerc, PctA, PctC, PctG, PctT) %>% dplyr::select(ReadPerc)
)

# The total read count from indels is not always the same as the total read count from snp data -- likely due to different pipelines?
# Only 1.8% of samples demonstrated to be larger in the SNP
# To ameliorate this the code is modified to just account for whichever one is larger.
# based on email conversation with Xuning Wang, author of CRISPR-DAV.
total_reads = inner_join(
    snps %>% aggregate(total ~ Sample, ., max) %>% dplyr::rename(SNPReadSum = total),
    indels %>% aggregate(ReadCount ~ Sample, ., sum) %>% dplyr::rename(IndelReadSum = ReadCount)) 
  
total_reads_indels = total_reads %>% dplyr::select(-SNPReadSum) %>% dplyr::rename(ReadSum = IndelReadSum)
total_reads_snps = total_reads %>% dplyr::select(-IndelReadSum) %>% dplyr::rename(ReadSum = SNPReadSum)

total_reads %<>%
  mutate(ReadSum = {ifelse(SNPReadSum > IndelReadSum, SNPReadSum, IndelReadSum)}) %<>%
  dplyr::select(Sample, ReadSum)

# Ammend the indel and snp data with the proper total read count per sample
#indels = indels %>% 
 # dplyr::select(-ReadPct) %>%
 # inner_join(., total_reads) %>%
 # mutate(ReadPct = 100*(ReadCount/ReadSum))

#snps_cleaned = snps_cleaned %>%
#  dplyr::select(-ReadPerc) %>%
#  inner_join(., total_reads) %>%
#  mutate(ReadPerc = 100*(ReadCount/ReadSum))
```

```{r, warning = FALSE, message = FALSE, echo = FALSE}
# Determine which samples failed
# The additional two are not being caught for some reason, so now they are added here.
failed_samples = total_reads_indels %>% filter(ReadSum < 250) %>% .$Sample   
complete_failed_samples = total_reads_indels %>% filter(ReadSum == 0) %>% .$Sample 

# Filter our completely failed samples
filtered_sample_information = sample_information %>% 
  filter(!(sample_name %in% complete_failed_samples))

failed_sample_information = sample_information %>% 
  filter(sample_name %in% complete_failed_samples)

# Establish a list of samples that worked
samples = filtered_sample_information$sample_name
crisprdav_sample_names = filtered_sample_information$Sample
```

```{r, include = FALSE}
# Clean the data with respect to polarity and base identity and position for graphing.
# Read the sense for each sample
# The senses for each sample is taken from the site.bed file generated by the CRISPR-DAV pipeline.
get_sense = function(sample){
paste0("/Users/kluesner/Desktop/Research/NGS/CRISPR-DAV/batch_analysis/", analysis_name, "/", sample, "/site.bed") %>% 
  read.delim2(., header = FALSE) %>%
  .$V6 %>% 
  as.character() %>%
  data.frame(senses = ., Sample = sample) %>% 
  return()
}

#sample_senses = lapply(X = crisprdav_sample_names, FUN = get_sense) %>%
#  ldply(., "data.frame") %>%
#  mutate(senses={ifelse(senses == "+", 1, -1)}) %>% 
#  inner_join(., sample_information) %>%
#  dplyr::select(sample_name, senses) %>%
#  dplyr::rename(Sample = sample_name)
sample_senses = sample_information %>% dplyr::select(sample_name, senses) %>% dplyr::rename(Sample = sample_name)

# Assign the antisense snp data to be used depending on the conditional guide matching later on.
# change_here: This code alters based on the specific analysis, will need to change for 'sample_information'.
snps_cleaned = data.frame(Sample = samples) %>%
  inner_join(., sample_senses) %>%
  inner_join(snps_cleaned, .) %>% 
  inner_join(., data.frame(base = ACGT, antibase = TGCA)) %>%
  inner_join(., data.frame(ref = ACGT, antiref = TGCA)) %>%
  inner_join(., sample_information %>% dplyr::select(-Sample) %>% dplyr::rename(Sample = sample_name))
```

```{r, include = FALSE}
# Function for reformatting the data to give the summary graphic
orient_data = function(sample){
summary_data = snps_cleaned %>%
  filter(Sample == sample) %>%
  mutate(rel_pos = {ifelse(senses == -1, 21-rel_pos, rel_pos)}) %>%
  mutate(base = {ifelse(senses == 1, base, as.character(antibase))}) %>%
  mutate(ref = {ifelse(senses == 1, ref, as.character(antiref))}) %>%
  filter(rel_pos > window_start & rel_pos <= window_end)

summary_data$base = factor(summary_data$base, levels = rev(ACGT))

# may need to change the 4 to the position where the 1 shows up.
if(summary_data$senses[1] == 1)
  {guide = summary_data$ref[1:(length(summary_data$ref)/4)]
   positions = c(window_start:-1, summary_data$rel_pos[4:(length(summary_data$rel_pos)/4)])} else
     {guide = as.character(rev(summary_data$ref[1:(length(summary_data$ref)/4)]))
      positions = c(window_start:-1, 1:window_end)}

return(summary_data)
}
```

```{r, include = FALSE}
# Summary plots
## Overall summary table
## Manually adjust samples
## Need to only go to 322 in the last code chunk for bioarxiv submission
isUsuable = function(x){is.na(!(class(tryCatch(orient_data(x), error = function(e) e)) == "error")[2])}
samples = samples[mapply(FUN = isUsuable, x = samples)]

summary_data = lapply(samples, orient_data) %>% plyr::ldply("data.frame")
```

```{r, echo = FALSE}
# Print Table
#knitr::kable(summary_table)
```

```{r, include = FALSE}
# Generate indel distribution function
generate_indel_distribution = function(sample){

indels_cleaned = indels %>%
  filter(Sample == sample) %>%
  aggregate(ReadPct ~ Sample*IndelLength, ., sum)

perc_wt = indels_cleaned %>% filter(IndelLength == 0) %>% .$ReadPct %>% round(., 2) %>% as.character
perc_tot_indel = indels_cleaned %>% filter(IndelLength != 0) %>% .$ReadPct %>% sum %>% round(., 2) %>% as.character
perc_OofF_indels = indels_cleaned[as.numeric(which(indels_cleaned[,2]%%3L!=0L)),] %>% .$ReadPct %>% sum %>% round(., 2) %>% as.character

plot = indels_cleaned %>%
  ggplot(aes(x = IndelLength, y = ReadPct)) +
  geom_bar(stat = "identity", fill = "#79A8D4", color = "black") +
  theme_bw() +
  ylab("Percent of Reads") + 
  xlab("Indel Length") +
  annotate(geom = "text", label = paste0("WT: ", perc_wt, "%"), x = -87.5, y = 90, size = 3) +
  annotate(geom = "text", label = paste0("Total Indels: ", perc_tot_indel, "%"), x = -80, y = 80, size = 3) +
  annotate(geom = "text", label = paste0("Frameshift Indels: ", perc_OofF_indels, "%"), x = -74.5, y = 70, size = 3) +
  ggtitle(sample) +
  scale_x_continuous(limits = c(-100,25), breaks = seq(-100,25,25)) +
  scale_y_continuous(limits = c(0,100), breaks = seq(0,100,20)) +
        theme(axis.ticks = element_blank(),
              axis.text.x=element_text(size=11, color = "black"),
              axis.text.y=element_text(size=11, color = "black"),
              axis.title.x=element_text(size=12, color = "black"),
              axis.title.y=element_text(size=12, color = "black"),
              axis.ticks.x=element_line(size=.5, color = "black"),
              axis.ticks.y=element_line(size=.5, color = "black"),
              plot.title = element_text(hjust = -.03, size = 10),
              panel.background = element_rect(fill = "transparent",colour = NA), # or theme_blank()
              plot.background = element_rect(fill = "transparent",colour = NA),
              aspect.ratio = 0.75#,
              #plot.margin = margin(10,10,10,10)
        ) +
  coord_cartesian(clip = "off")

return(plot)
}
```


```{r, include = FALSE}
# Generating table and bar plot function

generate_plot = function(sample, plot){
#sample = samples[1]; treatment = "Edited"

tile_plot_data = snps_cleaned %>%
  filter(Sample == sample) %>%
  mutate(rel_pos = {ifelse(senses == -1, 21-rel_pos, rel_pos)}) %>%
  mutate(base = {ifelse(senses == 1, base, as.character(antibase))}) %>%
  mutate(ref = {ifelse(senses == 1, ref, as.character(antiref))}) %>%
  filter(rel_pos > window_start & rel_pos <= window_end)

tile_plot_data$base = factor(tile_plot_data$base, levels = rev(ACGT))

if(tile_plot_data$senses[1] == 1)
    {guide = tile_plot_data$ref[1:(length(tile_plot_data$ref)/4)]
     #positions = c(window_start:-1, tile_plot_data$rel_pos[4:(length(tile_plot_data$rel_pos)/4)])
         positions = c(window_start:-1, 1:window_end)
     } else
     {guide = as.character(rev(tile_plot_data$ref[1:(length(tile_plot_data$ref)/4)]))
      positions = c(window_start:-1, 1:window_end)}

  x_labels = paste0(guide, "[", positions, "]")
  
perc_tot_indel = indels %>%
  filter(Sample == sample) %>%
  aggregate(ReadPct ~ Sample*IndelLength, ., sum) %>% 
  filter(IndelLength != 0) %>% 
  .$ReadPct %>% 
  sum

indel_color = color_fn(perc_tot_indel)

plotA = tile_plot_data %>%
  ggplot(aes(x = rel_pos, y = base, fill = ReadPerc)) + 
  geom_tile() +
  ggtitle(sample) +
  geom_rect(aes(xmin = 0.5, ymin = 0.5, xmax = 20.5, ymax = 4.5), color = "black", alpha = 0, lwd = 0.25) + # protospacer
  geom_rect(aes(xmin = window_start+0.5, ymin = 0.5, xmax = 0.5, ymax = 4.5), color = "black", alpha = 0, lwd = 0.25) + # upstream
  geom_rect(aes(xmin = 20.5, ymin = 0.5, xmax = window_end + 0.5, ymax = 4.5), color = "black", alpha = 0, lwd = 0.25) + # downstream
  scale_fill_gradientn(colours = c("#FFFFFF","#FBEDEC", "#EDA9A6", "#E3797D", "#BC656D", "#9988A3", "#79A8D4"), 
                       values = rescale(c(0,7.2, 33.3, 52,78.9,90, 100))) +
  geom_text(aes(label = round(ReadPerc, table_digits)), angle = 0, size = 2.5) +
  scale_x_discrete(limits = c((window_start+1):window_end), labels = c(parse(text = x_labels), "Indel"), position = "top") +
        guides(fill = FALSE) + 
       # scale_x_discrete(name = "test", breaks = 1, labels = "testes") + 
        labs(x = NULL, y = NULL) + 
  #annotate(geom = "text", x = -3, y = 2, label = "BE3 \n Site 1") +
        theme(axis.ticks = element_blank(),
              axis.line = element_blank(),
              axis.text.x=element_text(size=9, color = "black", margin = margin(t = -10)),
              axis.text.y=element_text(size=9, color = "black"),
              plot.title = element_text(hjust = -.03, size = 10),
              panel.background = element_rect(fill = "transparent",colour = NA), # or theme_blank()
              plot.background = element_rect(fill = "transparent",colour = NA),
              aspect.ratio = 1/13
        ) +
  coord_cartesian(clip = "off") +
  annotate(geom = "rect",
           xmin = window_end + 0.5, ymin = 3.5,
           xmax = window_end + 1.9, ymax = 4.5,
           fill = indel_color, color = "black", lwd = 0.25) +
  annotate(geom = "text", label = as.character(round(perc_tot_indel, table_digits)), x = window_end + 1.2, y = 4, size = 2.75) +
  annotate(geom = "text", label = "Indel", x = window_end + 1.2, y = 5, size = 2.75)
  
  


plotB = tile_plot_data %>%
  filter(base != ref) %>%
  ggplot(aes(x = rel_pos, y =  ReadPerc, fill = base)) +
  geom_bar(stat = "identity") +
  xlab("") + 
  ylab("Percent Alternative\nBasecall") +
  ggtitle(sample) +
  scale_x_discrete(limits = c((window_start+1):window_end), labels = parse(text = x_labels) , position = "bottom",
                   breaks = c((window_start+1):window_end)) +
  scale_y_continuous(limits = c(0,100), breaks = seq(0,100,20)) +
  #geom_rect(aes(xmin = 0.5, ymin = 0.5, xmax = 20.5, ymax = 100), color = "black", alpha = 0, lwd = 0.25) +
  #geom_rect(aes(xmin = -2.5, ymin = 0.5, xmax = 0.5, ymax = 100), color = "black", alpha = 0, lwd = 0.25) +
  theme_bw() +
  labs(fill="") +
  scale_fill_manual(values=c("A"="darkgreen", "C"="royalblue", "G"="darkgrey", "T"="firebrick3")) +
  theme(axis.text.x=element_text(size=11, color = "black"),
              axis.text.y=element_text(size=11, color = "black"),
              panel.background = element_rect(fill = "transparent",colour = NA), # or theme_blank()
              plot.background = element_rect(fill = "transparent",colour = NA),
              aspect.ratio = .18,
              legend.position=c(0.95,.55),
              legend.text = element_text(size = 12),
              axis.title.x=element_text(size=13, color = "black"),
              axis.title.y=element_text(size=13, color = "black"),
              plot.title = element_text(hjust = -.03, size = 12),
        ) +
  coord_cartesian(clip = "off") +
  geom_vline(xintercept = 20.5, color = "black") +
  geom_vline(xintercept = 0.5, color = "black")

plotC = NULL


if(plot == "bar"){return(plotB)} else {
  if(plot == "tile"){return(plotA)} else {
    return(plotC)
    
  }
}

}

#generate_plot("NKNGS-1-1", plot = "bar")
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
### Change the function used in all of the code chunks based on what plot you want
### i.e. plotA, plotB, or plotC
a = generate_indel_distribution(samples[1])
b = generate_indel_distribution(samples[2])
c = generate_indel_distribution(samples[3])
d = generate_indel_distribution(samples[4])
grid.arrange(a, b, c, d, ncol = 2)
```


```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[1])
b = generate_indel_distribution(samples[2])
c = generate_indel_distribution(samples[3])
d = generate_indel_distribution(samples[4])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[5])
b = generate_indel_distribution(samples[6])
c = generate_indel_distribution(samples[7])
d = generate_indel_distribution(samples[8])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[9])
b = generate_indel_distribution(samples[10])
c = generate_indel_distribution(samples[11])
d = generate_indel_distribution(samples[12])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[13])
b = generate_indel_distribution(samples[14])
c = generate_indel_distribution(samples[15])
d = generate_indel_distribution(samples[16])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[17])
b = generate_indel_distribution(samples[18])
c = generate_indel_distribution(samples[19])
d = generate_indel_distribution(samples[20])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[21])
b = generate_indel_distribution(samples[22])
c = generate_indel_distribution(samples[23])
d = generate_indel_distribution(samples[24])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[25])
b = generate_indel_distribution(samples[26])
c = generate_indel_distribution(samples[27])
d = generate_indel_distribution(samples[28])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[29])
b = generate_indel_distribution(samples[30])
c = generate_indel_distribution(samples[31])
d = generate_indel_distribution(samples[32])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[33])
b = generate_indel_distribution(samples[34])
c = generate_indel_distribution(samples[35])
d = generate_indel_distribution(samples[36])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[37])
b = generate_indel_distribution(samples[38])
c = generate_indel_distribution(samples[39])
d = generate_indel_distribution(samples[40])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[41])
b = generate_indel_distribution(samples[42])
c = generate_indel_distribution(samples[43])
d = generate_indel_distribution(samples[44])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[45])
b = generate_indel_distribution(samples[46])
c = generate_indel_distribution(samples[47])
d = generate_indel_distribution(samples[48])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[49])
b = generate_indel_distribution(samples[50])
c = generate_indel_distribution(samples[51])
d = generate_indel_distribution(samples[52])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[53])
b = generate_indel_distribution(samples[54])
c = generate_indel_distribution(samples[55])
d = generate_indel_distribution(samples[56])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[57])
b = generate_indel_distribution(samples[58])
c = generate_indel_distribution(samples[59])
d = generate_indel_distribution(samples[60])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[61])
b = generate_indel_distribution(samples[62])
c = generate_indel_distribution(samples[63])
d = generate_indel_distribution(samples[64])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[65])
b = generate_indel_distribution(samples[66])
c = generate_indel_distribution(samples[67])
d = generate_indel_distribution(samples[68])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[69])
b = generate_indel_distribution(samples[70])
c = generate_indel_distribution(samples[71])
d = generate_indel_distribution(samples[72])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[73])
b = generate_indel_distribution(samples[74])
c = generate_indel_distribution(samples[75])
d = generate_indel_distribution(samples[76])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[77])
b = generate_indel_distribution(samples[78])
c = generate_indel_distribution(samples[79])
d = generate_indel_distribution(samples[80])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[81])
b = generate_indel_distribution(samples[82])
c = generate_indel_distribution(samples[83])
d = generate_indel_distribution(samples[84])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[85])
b = generate_indel_distribution(samples[86])
c = generate_indel_distribution(samples[87])
d = generate_indel_distribution(samples[88])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[89])
b = generate_indel_distribution(samples[90])
c = generate_indel_distribution(samples[91])
d = generate_indel_distribution(samples[92])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[93])
b = generate_indel_distribution(samples[94])
c = generate_indel_distribution(samples[95])
d = generate_indel_distribution(samples[96])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[97])
b = generate_indel_distribution(samples[98])
c = generate_indel_distribution(samples[99])
d = generate_indel_distribution(samples[100])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[101])
b = generate_indel_distribution(samples[102])
c = generate_indel_distribution(samples[103])
d = generate_indel_distribution(samples[104])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[105])
b = generate_indel_distribution(samples[106])
c = generate_indel_distribution(samples[107])
d = generate_indel_distribution(samples[108])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[109])
b = generate_indel_distribution(samples[110])
c = generate_indel_distribution(samples[111])
d = generate_indel_distribution(samples[112])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[113])
b = generate_indel_distribution(samples[114])
c = generate_indel_distribution(samples[115])
d = generate_indel_distribution(samples[116])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[117])
b = generate_indel_distribution(samples[118])
c = generate_indel_distribution(samples[119])
d = generate_indel_distribution(samples[120])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[121])
b = generate_indel_distribution(samples[122])
c = generate_indel_distribution(samples[123])
d = generate_indel_distribution(samples[124])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[125])
b = generate_indel_distribution(samples[126])
c = generate_indel_distribution(samples[127])
d = generate_indel_distribution(samples[128])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[129])
b = generate_indel_distribution(samples[130])
c = generate_indel_distribution(samples[131])
d = generate_indel_distribution(samples[132])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[133])
b = generate_indel_distribution(samples[134])
c = generate_indel_distribution(samples[135])
d = generate_indel_distribution(samples[136])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[137])
b = generate_indel_distribution(samples[138])
c = generate_indel_distribution(samples[139])
d = generate_indel_distribution(samples[140])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[141])
b = generate_indel_distribution(samples[142])
c = generate_indel_distribution(samples[143])
d = generate_indel_distribution(samples[144])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[145])
b = generate_indel_distribution(samples[146])
c = generate_indel_distribution(samples[147])
d = generate_indel_distribution(samples[148])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[149])
b = generate_indel_distribution(samples[150])
c = generate_indel_distribution(samples[151])
d = generate_indel_distribution(samples[152])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[153])
b = generate_indel_distribution(samples[154])
c = generate_indel_distribution(samples[155])
d = generate_indel_distribution(samples[156])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[157])
b = generate_indel_distribution(samples[158])
c = generate_indel_distribution(samples[159])
d = generate_indel_distribution(samples[160])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[161])
b = generate_indel_distribution(samples[162])
c = generate_indel_distribution(samples[163])
d = generate_indel_distribution(samples[164])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[165])
b = generate_indel_distribution(samples[166])
c = generate_indel_distribution(samples[167])
d = generate_indel_distribution(samples[168])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[169])
b = generate_indel_distribution(samples[170])
c = generate_indel_distribution(samples[171])
d = generate_indel_distribution(samples[172])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[173])
b = generate_indel_distribution(samples[174])
c = generate_indel_distribution(samples[175])
d = generate_indel_distribution(samples[176])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[177])
b = generate_indel_distribution(samples[178])
c = generate_indel_distribution(samples[179])
d = generate_indel_distribution(samples[180])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[181])
b = generate_indel_distribution(samples[182])
c = generate_indel_distribution(samples[183])
d = generate_indel_distribution(samples[184])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[185])
b = generate_indel_distribution(samples[186])
c = generate_indel_distribution(samples[187])
d = generate_indel_distribution(samples[188])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[189])
b = generate_indel_distribution(samples[190])
c = generate_indel_distribution(samples[191])
d = generate_indel_distribution(samples[192])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[193])
b = generate_indel_distribution(samples[194])
c = generate_indel_distribution(samples[195])
d = generate_indel_distribution(samples[196])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[197])
b = generate_indel_distribution(samples[198])
c = generate_indel_distribution(samples[199])
d = generate_indel_distribution(samples[200])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[201])
b = generate_indel_distribution(samples[202])
c = generate_indel_distribution(samples[203])
d = generate_indel_distribution(samples[204])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[205])
b = generate_indel_distribution(samples[206])
c = generate_indel_distribution(samples[207])
d = generate_indel_distribution(samples[208])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[209])
b = generate_indel_distribution(samples[210])
c = generate_indel_distribution(samples[211])
d = generate_indel_distribution(samples[212])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[213])
b = generate_indel_distribution(samples[214])
c = generate_indel_distribution(samples[215])
d = generate_indel_distribution(samples[216])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[217])
b = generate_indel_distribution(samples[218])
c = generate_indel_distribution(samples[219])
d = generate_indel_distribution(samples[220])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[221])
b = generate_indel_distribution(samples[222])
c = generate_indel_distribution(samples[223])
d = generate_indel_distribution(samples[224])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[225])
b = generate_indel_distribution(samples[226])
c = generate_indel_distribution(samples[227])
d = generate_indel_distribution(samples[228])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[229])
b = generate_indel_distribution(samples[230])
c = generate_indel_distribution(samples[231])
d = generate_indel_distribution(samples[232])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[233])
b = generate_indel_distribution(samples[234])
c = generate_indel_distribution(samples[235])
d = generate_indel_distribution(samples[236])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[237])
b = generate_indel_distribution(samples[238])
c = generate_indel_distribution(samples[239])
d = generate_indel_distribution(samples[240])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[241])
b = generate_indel_distribution(samples[242])
c = generate_indel_distribution(samples[243])
d = generate_indel_distribution(samples[244])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[245])
b = generate_indel_distribution(samples[246])
c = generate_indel_distribution(samples[247])
d = generate_indel_distribution(samples[248])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[249])
b = generate_indel_distribution(samples[250])
c = generate_indel_distribution(samples[251])
d = generate_indel_distribution(samples[252])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[253])
b = generate_indel_distribution(samples[254])
c = generate_indel_distribution(samples[255])
d = generate_indel_distribution(samples[256])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[257])
b = generate_indel_distribution(samples[258])
c = generate_indel_distribution(samples[259])
d = generate_indel_distribution(samples[260])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[261])
b = generate_indel_distribution(samples[262])
c = generate_indel_distribution(samples[263])
d = generate_indel_distribution(samples[264])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[265])
b = generate_indel_distribution(samples[266])
c = generate_indel_distribution(samples[267])
d = generate_indel_distribution(samples[268])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[269])
b = generate_indel_distribution(samples[270])
c = generate_indel_distribution(samples[271])
d = generate_indel_distribution(samples[272])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[273])
b = generate_indel_distribution(samples[274])
c = generate_indel_distribution(samples[275])
d = generate_indel_distribution(samples[276])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[277])
b = generate_indel_distribution(samples[278])
c = generate_indel_distribution(samples[279])
d = generate_indel_distribution(samples[280])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[281])
b = generate_indel_distribution(samples[282])
c = generate_indel_distribution(samples[283])
d = generate_indel_distribution(samples[284])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[285])
b = generate_indel_distribution(samples[286])
c = generate_indel_distribution(samples[287])
d = generate_indel_distribution(samples[288])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[289])
b = generate_indel_distribution(samples[290])
c = generate_indel_distribution(samples[291])
d = generate_indel_distribution(samples[292])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[293])
b = generate_indel_distribution(samples[294])
c = generate_indel_distribution(samples[295])
d = generate_indel_distribution(samples[296])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[297])
b = generate_indel_distribution(samples[298])
c = generate_indel_distribution(samples[299])
d = generate_indel_distribution(samples[300])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[301])
b = generate_indel_distribution(samples[302])
c = generate_indel_distribution(samples[303])
d = generate_indel_distribution(samples[304])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[305])
b = generate_indel_distribution(samples[306])
c = generate_indel_distribution(samples[307])
d = generate_indel_distribution(samples[308])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[309])
b = generate_indel_distribution(samples[310])
c = generate_indel_distribution(samples[311])
d = generate_indel_distribution(samples[312])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[313])
b = generate_indel_distribution(samples[314])
c = generate_indel_distribution(samples[315])
d = generate_indel_distribution(samples[316])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[317])
b = generate_indel_distribution(samples[318])
c = generate_indel_distribution(samples[319])
d = generate_indel_distribution(samples[320])
grid.arrange(a, b, c, d, ncol = 2)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
a = generate_indel_distribution(samples[321])
b = generate_indel_distribution(samples[322])
grid.arrange(a, b, c, d, ncol = 2)
```

